---
title: "Whakatipu IPM example"
author: "Andrew Digby"
date: "`r Sys.Date()`"
toc: true
number-sections: true
format: 
  html:
    toc: true
    toc-depth: 4
    self-contained: true
    code-fold: true
    code-tools: true
    df-print: kable
    code-line-numbers: true
  pdf:
    geometry: 
      - top=30mm
      - left=30mm
execute:
  cache: false
  echo: false
  warning: false
  message: false
  freeze: true
editor:
  source
---

# Load packages

```{r}
#| label: load-packages
#| code-summary: "Packages"
#| message: false

library(tidyverse)

packages <- c("nimble", 
              "ggplot2", 
              "coda")
walk(packages, library, character.only = T)

theme_set(theme_minimal())
```

# Introduction

Integrated population model demonstration for the Whakatipu takahe, using simulated data. Uses `nimble` package.

## Structure

Population process:
    N[t+1] = S[t] * N[t] + R[t]
    where R[t] = λ[t] * nests[t] * J[t]

Adult survival:
    telemetry data -> estimate S[t]
    y[i,t] ~ Bernoulli(S[t])

Nest productivity:
    chicks[i,t] ~ Poisson(λ[t]) or observed counts
    λ[t] = mean chicks per nest

Juvenile survival:
    yearling_count[i,t+1] ~ Binomial(chicks[i,t], J[t])
    J[t] = juvenile survival probability. 
    chicks[i,t] = chicks fledged

Recruitment:
    R[t] = λ[t] * nests[t] * J[t]
    nests[t] = total nests (estimated from breeding pairs)


# Data

Use example parameters to simulate data.

## Parameters

```{r}
#| label: params
#| code-summary: "Parameters"
#| message: false

# Parameters
n_years <- 5
n_adults <- 50
n_nests <- 8 # nests monitored
true_S <- rep(0.85, n_years-1)   # adult survival
true_J <- rep(0.5, n_years-1)    # juvenile survival
true_lambda <- rep(2, n_years-1) # chicks per nest
true_N <- numeric(n_years)
true_N[1] <- 50
```

## Simulate data

```{r}
#| label: simulate_data
#| code-summary: "Simulate data"
#| message: false


# ---------------------------
# Simulate example data
# ---------------------------
set.seed(123)
# Population process
for(t in 1:(n_years-1)) {
  R <- true_lambda[t] * n_nests * true_J[t]
  true_N[t+1] <- rpois(1, true_N[t]*true_S[t] + R)
}

# Telemetry survival data
adult_survival <- matrix(NA, nrow=n_adults, ncol=n_years-1)
for(t in 1:(n_years-1)) {
  adult_survival[,t] <- rbinom(n_adults, 1, true_S[t])
}

# Nest productivity and yearling data
chicks <- numeric(n_nests*(n_years-1))
yearlings <- numeric(n_nests*(n_years-1))
nest_year_index <- numeric(n_nests*(n_years-1))
idx <- 1
for(t in 1:(n_years-1)) {
  for(i in 1:n_nests) {
    nest_year_index[idx] <- t
    chicks[idx] <- rpois(1, true_lambda[t])
    yearlings[idx] <- rbinom(1, chicks[idx], true_J[t])
    idx <- idx + 1
  }
}

# Counts
count <- true_N
```

# Integrated population model

## Define IPM

Define IPM in Nimble

```{r}
#| label: define_ipm
#| code-summary: "Define IPM"
#| message: false
# ---------------------------
# Define IPM in NIMBLE
# ---------------------------
ipm_code <- nimbleCode({
  for(t in 1:(n_years-1)) {
    S[t] ~ dbeta(2, 2)          # Adult survival
    J[t] ~ dbeta(2, 2)          # Juvenile survival
    lambda[t] ~ dnorm(2, 1)     # Mean chicks per nest
  }
  
  N[1] ~ dpois(init_N)
  for(t in 1:(n_years-1)) {
    R[t] <- lambda[t] * nests[t] * J[t]
    N[t+1] ~ dpois(N[t]*S[t] + R[t])
  }
  
  # Adult survival likelihood
  for(i in 1:n_adults) {
    for(t in 1:(n_years-1)) {
      y[i,t] ~ dbern(S[t])
    }
  }
  
  # Nest productivity and juvenile survival
  for(i in 1:n_nests_total) {
    chicks[i] ~ dpois(lambda[year_nest[i]])
    yearlings[i] ~ dbinom(J[year_nest[i]], chicks[i])
  }
  
  # Count data
  for(t in 1:n_years) {
    count[t] ~ dpois(N[t])
  }
})
```


## Prepare data

Prepare data and constants

```{r}
#| label: prep_data
#| code-summary: "Prepare data"
#| message: false

# ---------------------------
# Prepare data and constants
# ---------------------------
constants <- list(
  n_years = n_years,
  n_adults = n_adults,
  n_nests_total = length(chicks),
  nests = rep(n_nests, n_years-1),
  year_nest = nest_year_index
)

data <- list(
  y = adult_survival,
  chicks = chicks,
  yearlings = yearlings,
  count = count,
  init_N = count[1]
)

inits <- list(
  S = rep(0.8, n_years-1),
  J = rep(0.5, n_years-1),
  lambda = rep(2, n_years-1),
  N = count
)
```


## Run model

```{r}
#| label: run_ipm
#| code-summary: "Run IPM"
#| message: false
# ---------------------------
# Step 4: Build and run the model
# ---------------------------
ipm_model <- nimbleModel(code = ipm_code, data = data, constants = constants, inits = inits)
ipm_conf <- configureMCMC(ipm_model, monitors = c("S", "J", "lambda", "N"))
ipm_mcmc <- buildMCMC(ipm_conf)

Cmodel <- compileNimble(ipm_model)
Cmcmc <- compileNimble(ipm_mcmc, project = ipm_model)
samples <- runMCMC(Cmcmc, niter = 10000, nburnin = 2000, thin = 10)
```

# Results

## Print results

```{r}
#| label: print_results
#| code-summary: "Print results"
#| message: false

print(summary(samples))
```

## Plot results

### MCMC samples

```{r}
#| label: mcmc_samples
#| code-summary: "MCMC samples"
#| message: false

# Convert samples to mcmc object
mcmc_samples <- as.mcmc(samples)

# Quick summary
summary(mcmc_samples)
```

### Trace plots

```{r}
#| label: trace_plots
#| code-summary: "Trace plots"
#| message: false

par(mfrow=c(2,2))
traceplot(mcmc_samples[,grep('S', colnames(mcmc_samples))], main='Traceplot: Adult Survival (S)')
traceplot(mcmc_samples[,grep('J', colnames(mcmc_samples))], main='Traceplot: Juvenile Survival (J)')
traceplot(mcmc_samples[,grep('lambda', colnames(mcmc_samples))], main='Traceplot: Chicks per Nest (lambda)')
traceplot(mcmc_samples[,grep('N', colnames(mcmc_samples))], main='Traceplot: Population Size (N)')
```

### Density plots

```{r}
#| label: density_plots
#| code-summary: "Density plots"
#| message: false

# Density plots using ggplot2
posterior_df <- as.data.frame(mcmc_samples) 
# Remove [ and ] from column names
names(posterior_df) <- gsub("\\[|\\]", "", names(posterior_df))


ls_post_df <- posterior_df %>%
  pivot_longer(cols = S1:S4, names_to = 'Year', values_to = 'Survival')

# Adult survival
ggplot(ls_post_df, aes(x=Survival, colour = Year, fill = Year )) +
  geom_density(alpha=0.5) +
  geom_vline(xintercept = true_S, linetype = 'dotted') +
  labs(title='Posterior Distribution: Adult Survival', x='Adult survival', y='Density')

lj_post_df <- posterior_df %>%
  pivot_longer(cols = J1:J4, names_to = 'Year', values_to = 'Survival')

ggplot(lj_post_df, aes(x=Survival, colour = Year, fill = Year )) +
  geom_density(alpha=0.5) +
  geom_vline(xintercept = true_J, linetype = 'dotted') +
  labs(title='Posterior Distribution: Juvenile Survival', x='Survival', y='Density')

# Lambda (mean chicks per nest)
ll_post_df <- posterior_df %>%
  pivot_longer(cols = lambda1:lambda4, names_to = 'Year', values_to = 'Lambda')

ggplot(ll_post_df, aes(x=Lambda, colour = Year, fill = Year )) +
  geom_density(alpha=0.5) +
  geom_vline(xintercept = true_lambda, linetype = 'dotted') +
  labs(title='Posterior Distribution: mean chicks per nest', x='Mean chicks per nest', y='Density')




```